EuringPosterFigures

### 2021-08-17 ARCHIVE/documents/ARCHIVE/DraftReport.Rmd
repo reorganization

#rmse
rmse_vals <- post_meds %>% 
  merge(true_vals %>% dplyr::select(scenario, variable, Truth), by = c('scenario', 'variable')) %>%
  transform(rmse.temp = (value-Truth)^2) %>%
  group_by(Data, scenario, variable) %>%
  dplyr::summarize(rmse = sqrt(mean(rmse.temp)))

@@

<!-- From amanda: help: not sure if we need something like this since we have the equations above? -->
<!-- $$ \left[\begin{array} -->
<!-- {l} -->
<!-- N_{1,t+1} \sim \text{Binomial}(N_{1,t},~S_{1,t}) \\ -->
<!-- N_{ad,t+1} \sim \text{Binomial}(N_{ad,t},~S_{ad,t}) \\ -->
<!-- N_{Tot, t+1} = N_{1,t} + N_{ad,t} -->
<!-- \end{array}\right]  -->
<!-- $$  -->

The joint likelihood for the integrated population model is the product of the likelihoods for the three subcomponent models. In instances when one dataset is removed, informative priors are used in place of the data to inform each of the relevant parameters (Table 1).

[IPM joint likelihood equation]
The overall likelihood for this hierarchical state-space model can be described as the product of the state and observation process models:
$$L_{IPM}(\text{y}, ~CH, ~\text{NestStatus}, ~\text{Fledged}|~N_{1},~N_{ad}, ~\phi_1, ~\phi_{ad}, ~f, ~p_{mr}, ~p_s, ~\lambda_{\text{fledglings}}, ~\phi_n) \ = $$
$$L_{Abundance}(\text{y}| ~N_1, ~N_{ad}, ~{p_s}, ~\phi_1,~\phi_{ad}, ~f)\ \times$$
$$L_{Productivity}(\text{NestStatus}, ~\text{Fledged} | ~\phi_{n}, ~\lambda_{\text{fledglings}})\ \times$$
$$L_{Survival}(\text{y}|~\text{z}, ~\phi_{ad}, ~p_{mr})$$

*Simulation scenarios*  
We developed three versions of an IPM: 1) a "full" IPM that incorporates all three datasets (counts, productivity, mark-resight); 2) an IPM with the counts and productivity datasets only (excludes mark-resight dataset); and, 3) an IPM with the counts and mark-resight datasets only (excludes the productivity dataset). There are numerous scenarios we could run to vary detection and survival probabilities for each IPM version and test our objectives. We opted to run a select number of scenarios to provide preliminary findings to inform future work. For each version of the IPM, we ran 5 scenarios, for a total of 15 scenarios (Table for scenarios). Within each scenario, we varied the following parameters: mark-resight probability (0.3, 0.5, 0.8), count detection probability (0.3, 0.5, 0.85), and juvenile survival (0.3, 0.4, 0.5). The remaining parameters were kept constant for all scenarios: daily nest survival (0.975), mean clutch size (2.5), max nest age (30), initial age distribution (1000 juveniles, 1000 adults), and adult survival (0.77). For demographic parameters, we chose to vary juvenile survival because it is a hidden parameter, and these various values result in 5% annual decline, steady population growth, and 5% annual growth, respectively.

@@

*Estimation and diagnostics*   
<!-- amelia - just a quick draft, but is this right? -->
Models were ran in NIMBLE using program R (NIMBLE 2020). We ran 45,000 iterations with the first 5,000 as a burn-in. We thinned samples to reduce autocorrelation and retained every 10th sample, for a total of 4,000 samples. Model convergence was assessed visually using trace plots and the Brooks-Gelman-Rubin statistic (Rhat). We examined model performance using relative bias and root mean square error (RMSE).

>>>>

#rmse
rmse_vals <- post_meds %>% 
  merge(true_vals %>% dplyr::select(scenario, variable, Truth), by = c('scenario', 'variable')) %>%
  transform(rmse.temp = (value-Truth)^2) %>% #simulation level
  group_by(Data, scenario, variable) %>%
  dplyr::summarize(rmse = sqrt(mean(rmse.temp))) #scenario level

@@

<!-- From amanda: help: not sure if we need something like this since we have the equations above? aeb - we can use begin{align} if we want and put $~ or &= where we want things to be centered around, but I think this is good enough for now-->
<!-- $$ \left[\begin{array} -->
<!-- {l} -->
<!-- N_{1,t+1} \sim \text{Binomial}(N_{1,t},~S_{1,t}) \\ -->
<!-- N_{ad,t+1} \sim \text{Binomial}(N_{ad,t},~S_{ad,t}) \\ -->
<!-- N_{Tot, t+1} = N_{1,t} + N_{ad,t} -->
<!-- \end{array}\right]  -->
<!-- $$  -->

The joint likelihood for the integrated population model is the product of the likelihoods for the three subcomponent models. In instances when one dataset is removed, noninformative priors are used in place of the data to inform each of the relevant parameters.

[IPM joint likelihood equation] *is this how we want this?*
The overall likelihood for this hierarchical state-space model can be described as the product of the state and observation process models:
$$L_{IPM}(\text{y}, ~CH, ~\text{NestStatus}, ~\text{Fledged}|~N_{1},~N_{ad}, ~\phi_1, ~\phi_{ad}, ~f, ~p_{mr}, ~p_s, ~\lambda_{\text{fledglings}}, ~\phi_n) \ = $$
$$L_{Abundance}(\text{y}| ~N_1, ~N_{ad}, ~{p_s},~\phi_{ad}, ~f)\ \times$$
$$L_{Productivity}(\text{NestStatus}, ~\text{Fledged} | ~\phi_{n}, ~\lambda_{\text{fledglings}})\ \times$$
$$L_{Survival}(\text{y}|~\text{z}, ~\phi_{ad}, ~p_{mr})$$

*Simulation scenarios*  
We developed three versions of an IPM: 1) a "full" IPM that incorporates all three datasets (counts, productivity, mark-resight); 2) an IPM with the counts and productivity datasets only (excludes mark-resight dataset); and, 3) an IPM with the counts and mark-resight datasets only (excludes the productivity dataset) (Figure 3). There are numerous scenarios we could run to vary detection and survival probabilities for each IPM version and test our objectives. We opted to run a select number of scenarios to provide preliminary findings to inform future work. For each version of the IPM, we ran 5 scenarios, for a total of 15 scenarios (Table for scenarios). Within each scenario, we varied the following parameters: mark-resight probability (0.3, 0.5, 0.8), count detection probability (0.3, 0.5, 0.85), and juvenile survival (0.3, 0.4, 0.5). The remaining parameters were kept constant for all scenarios: daily nest survival (0.975), mean clutch size (2.5), max nest age (30), initial age distribution (1000 juveniles, 1000 adults), and adult survival (0.77). For demographic parameters, we chose to vary juvenile survival because it is a hidden parameter, and these various values result in 5% annual decline, a stable population size, and 5% annual growth, respectively.

*need a table here - table 1 for true values, table 2 for varied params*

*also have the three dags next to each other - figure 3*

@@

*Estimation and diagnostics*   
<!-- amelia - just a quick draft, but is this right? AEB checked - made one small fix -->
Models were ran in NIMBLE using program R (NIMBLE 2020). We ran 45,000 iterations with the first 35,000 as a burn-in. We thinned samples to reduce autocorrelation and retained every 10th sample, for a total of 1,000 samples. Model convergence was assessed visually using trace plots and the Brooks-Gelman-Rubin statistic (Rhat). We examined model performance using relative bias and root mean square error (RMSE).

### 2021-08-17 README.Rmd
repo reorganization

Something here about background?

# Scripts, current version
## 0 - preparing scenarios
### compute_time_calc.R
Code for approximating the total run time, given number of simulated datasets, number of parameter scenarios, computer cores, and estimated run time for each model.

@@

## 1 - simulating data
### IPM_sim_2.0function.R
Script contains two functions for simulating data: 'simPopTrajectory' and 'simData'. 
The 'simPopTrajectory' function simulates the true population trajectory by individual and age class, starting from the stable age distribution. Individual fates are retained throughout total number of years.

@@

## 3 - run models
### run_scenarios_helperFns.R
Script with functions and code to run NIMBLE models. Function 'marray' transforms the survival data capture histories to m-array format. MCMC settings in this script, with functions for each of the 4 models. Each model has a run model function that defines constants, initial values, data, parameters to monitor, and code to build/run the models in NIMBLE.

### run_scenarios.R
Script that pulls from the scripts above to run models in parallel and output results.

## 4 - process results
### 01_load_and_process_data.R
Script that checks the Gelman-Rubin convergence statistic for each output MCMC sample, then thins the chains to reduce file size and places the output into categories based on the population growth rate, $\lambda$.

### 02_compute_geom_means.R
Computes the geometric means for $\lambda$ in each MCMC output.

# Data
Contains true parameter scenarios used to simulate population trajectories and observation data, all viable parameter combinations in files '-.lam.combos.RDS' and the selected parameter combinations used to simulate data are in files '-.lam.params.RDS' *(where "-" is low, med, or high)*. Folders labeled '-Trajectories' contain the simulated population trajectories for each of the scenarios found in '-.lam.params.RDS'. Each simulated trajectory is labeled with the scenario and the simulation number for that scenario. For example, in the 'highTrajectory' folder: 'highpopTraj-1-2.RDS' corresponds to the first parameter scenario in 'high.lam.param.RDS' and is the second population trajectory simulated using those parameter values.

>>>>

Understanding the processes that control population dynamics in wild populations is a critical component of conservation and management but is frequently limited by missing demographic information, uncertainty, and temporally or spatially misaligned datasets (Schaub & Abadi 2011, Zipkin & Saunders 2017). Integrated population models (IPMs; Besbeas et al. 2002, Brooks et al. 2004) are an increasingly popular tool in ecology that can help overcome these limitations by combining disparate datasets in a single, unified analysis (Schaub & Abadi 2011). This approach can provide several advantages, such as improved precision (Schaub et al. 2007, Tavecchia 2009, Abadi et al. 2010) and the estimation of parameters that would otherwise be unidentifiable (Besbeas 2005, Schaub et al. 2007, Veran & Lebreton 2008), which is often the case for key demographic rates such as recruitment or immigration. These advances have practical benefits for resource managers that must make decisions based on limited available information. As IPMs become more widely used, however, it is critical that they are robustly evaluated. In particular, the limitations of the IPM framework are still underexplored, particularly in situations where available data are sparse, of poor quality, or when data to inform specific parameters are entirely absent.

Through a simulation analysis, we will identify monitoring programs and demographic scenarios where integrated population models may not lead to improved precision or return unbiased estimates of parameters that would otherwise be unidentifiable when certain datasets are excluded. We apply this simulation study to to a passerine bird life history. We assume all model assumptions are met and compare parameter estimation for a traditional IPM with data informing abundance (count data), survival (mark-recapture data), and reproductive output (nest monitoring data) to situations when either of the latter two datasets are omitted. In doing so, we will refine our understanding of the mechanisms underlying IPMs and can better identify when they may serve as a useful tool or might not be necessary or warrant the collection of additional data. Improving our understanding of the strengths and weaknesses of the IPM framework can provide helpful insights for the design and implementation of field survey programs so as to most efficiently make use of limited resources to inform management efforts aimed at monitoring or recovering species that are deemed ecosystem indicators or depleted and in need of conservation intervention.

# Scripts, current version

## 0 - preparing scenarios

### compute_time_calc.R
Code for approximating the total run time, given number of simulated datasets, number of parameter scenarios, computer cores, and estimated run time for each model.

@@

## 1 - simulating data

### IPM_sim_2.0function.R

Script contains two functions for simulating data: 'simPopTrajectory' and 'simData'.

The 'simPopTrajectory' function simulates the true population trajectory by individual and age class, starting from the stable age distribution. Individual fates are retained throughout total number of years.

@@

## 3 - run models

### run_scenarios_helperFns.R

Script with functions and code to run NIMBLE models. Function 'marray' transforms the survival data capture histories to m-array format. MCMC settings in this script, with functions for each of the 4 models. Each model has a run model function that defines constants, initial values, data, parameters to monitor, and code to build/run the models in NIMBLE.

### run_scenarios.R

Main workhorse script that pulls from the scripts above to run models in parallel and output results.

## 4 - process results

### 01_load_and_process_data.R

Script that checks the Gelman-Rubin convergence statistic for each output MCMC sample, then thins the chains to reduce file size and places the output into categories based on the population growth rate, $\lambda$.

### 02_compute_geom_means.R

Computes the geometric means for $\lambda$ in each MCMC output.

# Data

Contains true parameter scenarios used to simulate population trajectories and observation data, all viable parameter combinations in files '-.lam.combos.RDS' and the selected parameter combinations used to simulate data are in files '-.lam.params.RDS' *(where "-" is low, med, or high)*. Folders labeled '-Trajectories' contain the simulated population trajectories for each of the scenarios found in '-.lam.params.RDS'. Each simulated trajectory is labeled with the scenario and the simulation number for that scenario. For example, in the 'highTrajectory' folder: 'highpopTraj-1-2.RDS' corresponds to the first parameter scenario in 'high.lam.param.RDS' and is the second population trajectory simulated using those parameter values.

### 2021-08-17 figures/ARCHIVE/EuringPosterFigures.Rmd
repo reorganization

library(tidyr)
library(dplyr)
library(cowplot)
library(ggplot2)
library(coda)
library(captioner)
library(knitr)
library(reshape2)
library(here)
library(RColorBrewer)
library(colorspace)
```

@@

# plot; use me - overview
ggplot(rel.bias, aes(x = factor(simscenarios), y = variable, fill = mean.rel.bias)) +
  geom_tile(color = 'grey50') +
  xlab('Detection level') + ylab('') +
  facet_grid(~lambda.scenario, drop = T, scales = 'free_x') +
  scale_fill_gradient2(name = "Relative bias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                     mid = "#f7f7f7", low = "royalblue4", high = "orange2", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
  theme_minimal() +
  theme(legend.position = 'top',
             strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"))

@@

```{r phiad}
pal1 <- diverging_hcl(n = 7, palette = "Blue-Yellow 3")
phiad <- rel.bias.vals %>% filter(variable == 'Adult survival')
summary(phiad$value)

p1 <- ggplot(rel.bias.vals %>% filter(variable == 'Adult survival'), 
             aes(x = factor(phiad.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Adult Survival') + ylab("") +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "white", low = "#9FA2FF", high = "#BAAE00", midpoint = 0,
                      breaks = c(-0.15, -0.05, 0, 0.05), n.breaks = 4, labels = c("-0.15", "-0.05", "0", "0.05")) +
  theme_light() +
  theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA),
        axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  ggtitle("Adult Survival")
p1
```

@@

p2 <- ggplot(rel.bias.vals %>% filter(variable == 'Juv survival'), 
             aes(x = factor(phi1.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Juvenile Survival') + ylab("") +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "white", low = "#11C638", high = "#EF9708", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2, 0.5, 0.8), n.breaks = 5, 
                      labels = c("-0.2", "0", "0.2", "0.5", "0.8")) +
  theme_light() +
  theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA),
        axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  ggtitle("Juvenile Survival")
p2
```

@@

p3 <- ggplot(rel.bias.vals %>% filter(variable == 'Fecundity'), 
             aes(x = factor(fec.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('True Fecundity') + ylab("") +
  facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
    scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0,
                      breaks = c(-0.4, -0.2, 0, 0.2), n.breaks = 4, 
                      labels = c("-0.4", "-0.2", "0", "0.2")) +
  theme_light() +
  theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA),
        axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  ggtitle("Fecundity")
p3
```

```{r combo}
library(patchwork)
plot1 <- p1 / p2 / p3
plot1

## export out
pdf(here("figures", "params_bias.pdf"), width = 12, height = 8)
plot_grid(p1, p2, p3, nrow = 3)
dev.off()
```

>>>>

library(tidyr)
library(dplyr)
library(cowplot)
library(ggplot2)
library(coda)
library(captioner)
library(knitr)
library(reshape2)
library(here)
library(RColorBrewer)
library(colorspace)
library(ggh4x)
```

@@

# plot; use me - overview
## change factor levels
rel.bias$variable <- factor(rel.bias$variable, levels = c("Adult survival", "Juv survival", "Fecundity"),
                            ordered = TRUE, labels = c("Adult Survival", "Juvenile Survival", "Fecundity"))

rel.bias$lambda.scenario <- factor(rel.bias$lambda.scenario, levels = c("Decreasing", "Stable", "Increasing"),
                                ordered = TRUE, labels = c(expression(paste("Decreasing ", lambda)), 
                                                           expression(paste("Stable ", lambda)), 
                                                           expression(paste("Increasing ", lambda))))
# rel.bias$simscenarios <- factor(rel.bias$simscenarios, levels = c("L", "M", "H"),
#                                 ordered = TRUE, labels = c(expression(paste("low ", italic(p))), 
#                                                            expression(paste("med ", italic(p))), 
#                                                            expression(paste("high ", italic(p)))))

## color palette
pal <- diverging_hcl(n = 7, palette = "Cyan-Magenta")

## plotting
ov <- ggplot(rel.bias, aes(x = factor(simscenarios), y = variable, fill = mean.rel.bias)) +
  geom_tile(color = 'grey50') +
  xlab('') + ylab('') +
  facet_grid(~lambda.scenario, drop = T, scales = 'free_x', labeller = label_parsed) +
  scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                     mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0,
                      breaks = c(-0.2, 0, 0.2), n.breaks = 3, labels = c("-0.2", "0", "0.2")) +
 scale_x_discrete(labels = c(expression(paste("low ", italic(p))), 
                             expression(paste("med ", italic(p))), 
                             expression(paste("high ", italic(p))))) +
  theme_light() +
  theme(legend.position = 'top',
        #axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 0, vjust = 1.5),
         panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line")) +
        # ggh4x.facet.nestline = element_line(size = 0.5)) +
        # panel.spacing = unit(1, "lines")) +
  ggtitle("") 
ov

## export out
ggsave(filename = here("figures", "overview_params_bias.pdf"), plot = ov)
```

@@

```{r phiad}
pal1 <- diverging_hcl(n = 7, palette = "Blue-Yellow 3")
phiad <- rel.bias.vals %>% filter(variable == 'Adult survival') 
summary(phiad$value) # look at range for scale

## fix faceted labels
rel.bias.vals$lambda.scenario <- factor(rel.bias.vals$lambda.scenario, levels = c("Decreasing", "Stable", "Increasing"),
                                ordered = TRUE, labels = c(expression(paste("Decreasing ", lambda)), 
                                                           expression(paste("Stable ", lambda)), 
                                                           expression(paste("Increasing ", lambda))))
rel.bias.vals$simscenarios <- factor(rel.bias.vals$simscenarios, levels = c("L", "M", "H"),
                                ordered = TRUE, labels = c(expression(paste("low ", italic(p))), 
                                                           expression(paste("med ", italic(p))), 
                                                           expression(paste("high ", italic(p)))))

p1 <- ggplot(rel.bias.vals %>% filter(variable == 'Adult survival'),
             aes(x = factor(phiad.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('\nTrue Adult Survival') + ylab("") +
  # facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
  facet_nested(~lambda.scenario+simscenarios, drop = T, scales = 'free_x', labeller = label_parsed,
               nest_line = TRUE) +
    scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      # mid = "white", low = "#9FA2FF", high = "#BAAE00", midpoint = 0,
                      mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0, 
                      breaks = c(-0.15, -0.05, 0, 0.05), n.breaks = 4, labels = c("-0.15", "-0.05", "0", "0.05")) +
  theme_light() +
  theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 90, vjust = 1.5),
        ggh4x.facet.nestline = element_line(size = 0.5),
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line")) +
        # panel.spacing = unit(1, "lines")) +
  ggtitle("Adult Survival")
p1
```

@@

p2 <- ggplot(rel.bias.vals %>% filter(variable == 'Juv survival'), 
             aes(x = factor(phi1.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('\nTrue Juvenile Survival') + ylab("") +
  # facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
  facet_nested(~lambda.scenario+simscenarios, drop = T, scales = 'free_x', labeller = label_parsed,
               nest_line = TRUE) +
  scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      # mid = "white", low = "#11C638", high = "#EF9708", midpoint = 0,
                      mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0, 
                      breaks = c(-0.2, 0, 0.2, 0.5, 0.8), n.breaks = 5, 
                      labels = c("-0.2", "0", "0.2", "0.5", "0.8")) +
  theme_light() +
 theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 90, vjust = 1.5),
        ggh4x.facet.nestline = element_line(size = 0.5),
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line")) +
        # panel.spacing = unit(1, "lines")) +
  ggtitle("Juvenile Survival")
p2
```

@@

p3 <- ggplot(rel.bias.vals %>% filter(variable == 'Fecundity'), 
             aes(x = factor(fec.true), y = variable, fill = value)) +
  geom_tile(color = 'grey50') +
  xlab('\nTrue Fecundity') + ylab("") +
  # facet_grid(~lambda.scenario+simscenarios, drop = T, scales = 'free_x') +
  facet_nested(~lambda.scenario+simscenarios, drop = T, scales = 'free_x', labeller = label_parsed,
               nest_line = TRUE) +
  scale_fill_gradient2(name = "Relative\nbias",
                      # mid = "#f7f7f7", low = "#a1d76a", high = "#e9a3c9", midpoint = 0,
                      # mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0,
                      mid = "white", low = "#0FCFC0", high = "#F79CD4", midpoint = 0, 
                      breaks = c(-0.4, -0.2, 0, 0.2), n.breaks = 4, 
                      labels = c("-0.4", "-0.2", "0", "0.2")) +
  theme_light() +
  theme(legend.position = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_rect(fill = "#EEEEEE", color = "#FFFFFF"),
        strip.text.x = element_text(face = "bold", color = "black"),
        strip.background = element_rect(fill = NA, color = "black"),
        axis.text.x = element_text(angle = 90, vjust = 1.5),
        ggh4x.facet.nestline = element_line(size = 0.5),
        panel.border = element_rect(color = "black", fill = NA),  
        panel.spacing.x = unit(0.75, "line")) +
        # panel.spacing = unit(1, "lines")) +
  ggtitle("Fecundity")
p3
```

```{r combo}
## export out
pdf(here("figures", "params_bias.pdf"), width = 12, height = 8)
plot_grid(p3, p2, p1, nrow = 3)
dev.off()

## try with overview plot
all <- ov + (p3/p2/p1)
ggsave(filename = here("figures", "all_bias.pdf"), plot = all, width = 22, height = 12)
#use # for spaces with missing plots
# layout_string <- 'A#BB
#                   ##CC
#                   ##DD'
# junk <- ov + (p3/p2/p1) + plot_layout(design=layout_string,
#                               widths=c(3,1,5,6),
#                               heights=c(5,3))
```

### 2021-08-17 figures/PaperFigures.Rmd
repo reorganization

#get posterior medians
# all.meds <- all.dat %>%
#   dplyr::select('phi1.obs', 'phi1.true', 'phiad.obs', 'phiad.true', 'fec.obs', 'fec.true',
#                 'p.surv', 'mean.p',
#                             'sims', 'scenario', 'simscenarios', 'lambda.scenario') %>%
#   reshape2::melt(id.vars = c('lambda.scenario', 'sims', 'scenario', 'simscenarios')) %>%
#   group_by(lambda.scenario, scenario, simscenarios, variable) %>%
#   summarize(median = median(value), .groups = 'keep') %>%
#   reshape2::dcast(lambda.scenario + scenario + simscenarios ~ variable, value.var = 'median') %>%
#   merge(scenarios %>% dplyr::select(-c(n.viable.combinations, priority)), by = c('simscenarios'))
# 
# 
# write.csv(all.meds, here::here('figures', 'Processed csvs', 'all.meds.csv'), row.names = F)

@@

##bias
rel.bias <- all.meds %>%
  transform(p.surv.true = ifelse(det.abund == 'L', 0.3))
  #calculate relative bias, mean across scenarios
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true) %>%
  dplyr::select('lambda.scenario', 'scenario',
                'phi1.bias', 'phiad.bias', 'fec.bias', 'det.MR', 'det.abund', 'det.prod') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'det.MR', 'det.abund', 'det.prod')) %>%
  group_by(lambda.scenario, det.MR, det.abund, det.prod, variable) %>%
  dplyr::summarize(bias = mean(value), .groups = 'keep') %>%
  transform(variable = factor(variable, levels = c('phiad.bias', 'phi1.bias', 'fec.bias'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity'))) %>%
  transform(lambda.scenario = factor(lambda.scenario,
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(det.MR = factor(det.MR, levels = c('L', 'M', 'H'))) %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H'))) %>%
  transform(det.prod = factor(det.prod, levels = c('L', 'M', 'H'))) %>%
  transform(missing.MR = ifelse(is.na(det.MR), 1, 0),
            missing.prod = ifelse(is.na(det.prod), 1, 0)) %>%
  transform(num.miss = missing.MR + missing.prod) %>%
  transform(dataset = ifelse(is.na(det.MR)&!is.na(det.prod), 'Counts+Prod', 
                             ifelse(!is.na(det.MR)&is.na(det.prod), 'Counts+MR',
                                    ifelse(is.na(det.MR)&is.na(det.prod), 'Counts', 'Full'))))

>>>>

#get posterior medians
# all.meds <- all.dat %>%
#   dplyr::select('phi1.obs', 'phi1.true', 'phiad.obs', 'phiad.true', 'fec.obs', 'fec.true',
#                             'sims', 'scenario', 'simscenarios', 'lambda.scenario') %>%
#   reshape2::melt(id.vars = c('lambda.scenario', 'sims', 'scenario', 'simscenarios')) %>%
#   group_by(lambda.scenario, scenario, simscenarios, variable) %>%
#   summarize(median = median(value), .groups = 'keep') %>%
#   reshape2::dcast(lambda.scenario + scenario + simscenarios ~ variable, value.var = 'median') %>%
#   merge(scenarios %>% dplyr::select(-c(n.viable.combinations, priority)), by = c('simscenarios'))
# 
# 
# write.csv(all.meds, here::here('results', 'Processed csvs', 'all.meds.csv'), row.names = F)

@@

# #just bias
rel.bias <- all.meds %>%
  #calculate relative bias, mean across scenarios
  transform(phi1.bias = (phi1.obs-phi1.true)/phi1.true,
            phiad.bias = (phiad.obs-phiad.true)/phiad.true,
            fec.bias = (fec.obs-fec.true)/fec.true) %>%
  dplyr::select('lambda.scenario', 'scenario',
                'phi1.bias', 'phiad.bias', 'fec.bias', 'det.MR', 'det.abund', 'det.prod') %>%
  reshape2::melt(id.vars = c('lambda.scenario', 'scenario', 'det.MR', 'det.abund', 'det.prod')) %>%
  group_by(lambda.scenario, det.MR, det.abund, det.prod, variable) %>%
  dplyr::summarize(bias = mean(value), .groups = 'keep') %>%
  transform(variable = factor(variable, levels = c('phiad.bias', 'phi1.bias', 'fec.bias'),
                              labels = c('Adult survival', 'Juv survival', 'Fecundity'))) %>%
  transform(lambda.scenario = factor(lambda.scenario,
                                     levels = c("Decreasing", "Stable", "Increasing"))) %>%
  transform(det.MR = factor(det.MR, levels = c('L', 'M', 'H'))) %>%
  transform(det.abund = factor(det.abund, levels = c('L', 'M', 'H'))) %>%
  transform(det.prod = factor(det.prod, levels = c('L', 'M', 'H'))) %>%
  transform(missing.MR = ifelse(is.na(det.MR), 1, 0),
            missing.prod = ifelse(is.na(det.prod), 1, 0)) %>%
  transform(num.miss = missing.MR + missing.prod) %>%
  transform(dataset = ifelse(is.na(det.MR)&!is.na(det.prod), 'Counts+Prod', 
                             ifelse(!is.na(det.MR)&is.na(det.prod), 'Counts+MR',
                                    ifelse(is.na(det.MR)&is.na(det.prod), 'Counts', 'Full'))))
